---
title: "Algorithmic Trading"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Firms have been forced to invest significantly in their trading and processing infrastructure by the increase in competition for lower transaction costs. However, without using automatic execution, a broker cannot conduct such giant order flow.  For large brokerage firms,  they benefit from algorithmic trading in competitions for lower-cost executions.  That's why algorithmic trading emerged. 

Algorithmic trading originated on proprietary trading desks of investment banking firms. It is a solution for smaller spreads and market and market fragmentation. It is also capable of slicing large parent orders ensuring that each child order gets the best price. Traders can benefit from this process to complet large orders without disturbing the market.  Current trading technology can decide the way they buy and sell. As the development of Data Science, advanced algorithms are capable of providing more choices.


# Moving Average
Moving average is a basic indicator to analyse price trend and momentumn. In R, packages to fix financial time series like "zoo", "xts" and "quantmod" are useful tools for traders.
We take the stock AAPL from 2015-09-26 to 2016-09-26 as data.

## Plot Simple Moving Average

### Plot Simple Moving Average by quantmod
```{r data, echo=FALSE, warning=FALSE, message=FALSE, results="hide", fig.keep ='none'}
library("RCurl")
library("xts")
library("TTR")
library("zoo")
library("PerformanceAnalytics")
library("Quandl")
library("quantmod")
library('urca')
library('tseries')

data <- getSymbols("AAPL")
Close <- Cl(AAPL)
high.close <- seriesHi(Close)
low.close <- seriesLo(Close)
data.aapl <- AAPL['2015-09-26::2016-09-26'] 
data.close <- Cl(data.aapl)
#barChart(data.aapl)
#candleChart(data.aapl,theme = "white")
par(mfrow = c(1,1))
chartSeries(data.aapl,theme = "white")
addSMA(n = 10)
addSMA(n = 50, col = 'blue')
addSMA(n = 100, col = 'green')
```

```{r, echo=FALSE, warning=FALSE}
addSMA(n = 100, col = 'green')
```

### Plot Simple Moving Average by Simple Plot
Two key functions of moving average are identifying trend and momentum. If a moving average is above the price, the stock is in an uptrend. In contrast, when a moving average is below the price, the stock is in downtrend. As for momentum, which refers to the rate of change on price movements, moving averages are used to represent short-term (less than 20 days), medium-term (20 to 100 days) and long-term (more than 100 days) price movements. Strong upward momentum is seen when shorter-term averages are located above longer-term averages and the two averages are diverging. Converse things in contrast.
```{r moving average by hand, echo=FALSE, warning= FALSE}
data.quandl.aapl <- Quandl("YAHOO/AAPL", start_date="2015-09-28", end_date="2016-09-26")
data.quandl.close <- data.quandl.aapl[nrow(data.quandl.aapl):1,]$Close

##Date
td <- data.quandl.aapl[nrow(data.quandl.aapl):1,]$Date

##Simple Moving Average
sma10 <- filter(data.quandl.close, rep(1/10, 10), sides = 1)
sma20 <- filter(data.quandl.close, rep(1/20, 20), sides = 1)
sma50 <- filter(data.quandl.close, rep(1/50, 50), sides = 1)
sma100 <- filter(data.quandl.close, rep(1/100, 100), sides = 1)
sma200 <- filter(data.quandl.close, rep(1/200, 200), sides = 1)

##Time series by zoo
data.quandl.close.ts <- zoo(x = data.quandl.close, order.by = td)

##Change sma to time series
s10 <- zoo(x = sma10, order.by = td)
s20 <- zoo(x = sma20, order.by = td)
s50 <- zoo(x = sma50, order.by = td)
s100 <- zoo(x = sma100, order.by = td)
s200 <- zoo(x = sma200, order.by = td)

##Plot sma
plot(data.quandl.close.ts, type = "l", main = "AAPL Moving Average from 2015-09-28 to 2015-09-26", xlab = "Date", ylab = "AAPL Price")
lines(s10, col = 2)
lines(s20, col = 3)
lines(s50, col = 6)
lines(s100, col = 4)
lines(s200, col = 5)
legend("bottomleft", c("SMA10","SMA20","SMA50","SMA100","SMA200"), col = c(2,3,6,4,5), lty = rep(1,5), pt.cex = 0.8, cex = rep(0.5,5))

```

## Exponential Moving Average Function and Plot
EMA is calculated by :
$$(close \,\, price-previous \,\,  EMA)*multiplier + current \,\,  EMA$$
$$multiplier = (2/(period \,\,  of  \,\, MA + 1))$$
Since recent prices are responsable more in EMA, EMA is more sensitive than SMA.
```{r exponential moving average, echo = TRUE, warning= FALSE}
ema <- function(sma, close.ema, timeperiod)
{
   multiplier <- (2/(timeperiod + 1))
   ema <- rep(0,length(sma))
   initial <- sma[timeperiod]
   
   ema[1:timeperiod-1] <- NA
   ema[timeperiod] <- initial
   
   for (i in timeperiod+1:length(sma)-1)
   {
     ema[i+1] <- (close.ema[i] - ema[i])*multiplier + ema[i]
   }
   return(ema[1:length(sma)])
   
}

ema20 <- zoo(ema(s20, data.quandl.close.ts, 20), order.by = td)
plot(data.quandl.close.ts, type = "l", main = "AAPL Moving Average from 2015-09-28 to 2016-09-26", xlab = "Date", ylab = "AAPL Price")
lines(ema20, col = 2)
lines(s20, col = 3)
legend("bottomleft", c("SMA20","EMA20"), col = c(3,2), lty = rep(1,2), pt.cex = 0.8, cex = rep(0.5,2))
```

### Ploting EMA20 by quantmod
```{r, results="hide", echo = TRUE, fig.keep ='none'}
chartSeries(data.aapl,theme = "white")

```


```{r, echo = TRUE}
addEMA()
```

## Function to Choose Long or Short Position
By using simple moving average, a function is created to indicate crossovers, that is, long or short position. They can be used to determine if prices are relatively high or low. Other indicators should be used with them.
```{r automatic indicators, echo = TRUE}
##=======================================
##Using simple moving average to decide long or short position.
##sma1 : ts; shorter-term moving average
##sma2 : ts; longer-term moving average
##price : ts; stock prices
##=======================================
long_short <- function(sma1, sma2, price)
{ 
  for (i in c(2:length(sma1)-1))
  {##eliminate effects of NA
    if((is.na(sma1[i]) == TRUE) || (is.na(sma2[i]) == TRUE))
    {next}
    if(sma1[i] != sma2[i])
    { 
      if((sma1[i] < sma2[i]) && (sma1[i+1] > sma2[i+1]))
      {
        cat("Long position at", toString(index(sma1[i+1])), "\n", "The price is", coredata(price[i+1]), "\n")
      }
      if((sma1[i] > sma2[i]) && (sma1[i+1] < sma2[i+1]))
      {
        cat("Short position at", toString(index(sma1[i+1])), "\n", "The price is", coredata(price[i+1]), "\n")
      }
    }
    else
    {sprintf("Crossover at %s. The price is %f", index(sma1[i]), coredata(price[i]))}
  }
}

long_short(s10, s20, data.quandl.close.ts)

```

## Bollinger Bands for Simple Moving Average
Bollinger bands, which are placed two standard deviations away from a simple moving average, were invented to detect dynamic volitality. The formula is : $$Upper\,\, Bollinger\,\, Bands = moving \,\,average + 2*standard\,\, deviation$$
$$Lower\,\, Bollinger\,\, Bands = moving\,\, average - 2*standard\,\, deviation$$
$$Middle\,\, Bollinger\,\, Bands = moving\,\, average$$

```{r bollinger band, echo = TRUE, warning=F}
bolband <- function(sma, day)
##============================
##sma : simple moving average
##day : period
##============================
{
   sd <- rollapply(sma, width = day, FUN = sd, fill = NA, align = "right")
   upperbol <- sma + 2*sd
   lowerbol <- sma - 2*sd
   return(list('upper' = upperbol, 'lower' = lowerbol))
}
bb <- bolband(s20, 20)
##plot bollinger average
plot(data.quandl.close.ts, type = "l", main = "AAPL Moving Average from 2015-09-28 to 2016-09-26", xlab = "Date", ylab = "AAPL Price")
lines(s20, col = 3)
lines(bb$upper, col = 2)
lines(bb$lower, col = 2)
legend("topright", c("SMA20","Bollinger Bands"), col = c(3,2), lty = rep(1,2), pt.cex = 0.8, cex = rep(0.5,2))
```

### Ploting Bollinger Bands by quantmod
```{r,echo = TRUE, results="hide", warning=F, fig.keep ='none'}
chartSeries(data.aapl,theme = "white")
```


```{r, echo = TRUE, warning=F}

addBBands()
```

## Function and Plot of MACD (Moving Average Convergence and Divergence)
MACD is calculated by substracting 26-day EMA from 12-day EMA. Signal is 9-day EMA of the MACD. The MACD oscillates above and below the zero line, which is also known as the centerline. These crossovers signal that the 12-day EMA has crossed the 26-day EMA. Positive MACD means that the momentum is upward.  A bullish crossover occurs when the MACD turns up and crosses above the signal line. 
```{r MACD, echo=FALSE, warning=F}
macd <- function(s12, s26, close.macd)
{
  ema12 <- ema(s12, close.macd, 12)
  ema26 <- ema(s26, close.macd, 26)
  macd <- ema12-ema26
  return(macd)
}
##sam12 and 26
sma9 <- filter(data.quandl.close, rep(1/9, 9),sides = 1)
sma12 <- filter(data.quandl.close, rep(1/12, 12),sides = 1)
sma26 <- filter(data.quandl.close, rep(1/26, 26),sides = 1)

s9 <- zoo(x = sma9, order.by = td)
s12 <- zoo(x = sma12, order.by = td)
s26 <- zoo(x = sma26, order.by = td)
##MACD
macd <- macd(s12, s26, data.quandl.close.ts)
##Signal 9-day EMA of the MACD
timeperiod <- 26
multiplier <- (2/(9 + 1))
ema9.macd <- rep(0,length(s9))
initial <- s9[26]
   
ema9.macd[1:timeperiod-1] <- NA
ema9.macd[timeperiod] <- initial
   
   for (i in timeperiod+1:length(s9)-1)
   {
     ema9.macd[i+1] <- (macd[i] - ema9.macd[i])*multiplier + ema9.macd[i]
   }
##Plot
plot(macd, type = "l", main = "AAPL Moving Average Convergence Divergence from 2015-09-28 to 2016-09-26", xlab = "Date", ylab = "MACD", col = 2)
abline(h=0, col = "green")
lines(ema9.macd, col = 4)
legend("bottomleft", c("MACD","Signal"), col = c(2,4), lty = rep(1,2), pt.cex = 0.8, cex = rep(0.5,2))
```

### Plot MACD by quantmod
```{r, echo=F, results="hide", warning=F}
chartSeries(data.aapl, theme = "white")
addMACD()
```


# VWAP

The volume weighted average price (VWAP) is a trading benchmark. It is the total traded value divided by the total traded volume. It is usually used by mutual funds, institutional investors and in pension plans in order not to disturb the market dynamics. That is, the aim of VWAP is to minimise the overall market impact and reduce the effect trading has on the asset's price.   
We take intraday 1-minute data of AAPL at 2016-10-04 as data.

## Getting intraday 1-minute data of AAPL at 2016-10-04 from Google Finance
There is no cleaned intraday data which can be download from R directly, so munging data from Google Finance is necessary.
```{r intraday data aapl, echo=FALSE, warning=FALSE, message=FALSE, results="hide"}
##online google finance query, i = 61, p = 2d
tmp.raw <- getURL('https://www.google.com/finance/getprices?i=61&p=3d&f=d,o,h,l,c,v&df=cpct&q=AAPL')
tmp.split <- strsplit(tmp.raw,'\n')
tmp.split.2 <- strsplit(tmp.split[[1]][-c(1:8)], ',')
tmp.bind <-do.call('rbind',tmp.split.2)
tmp <- apply(tmp.bind, 2, as.numeric)
tmp.na <- apply(tmp, 2, function(x) which(is.na(x)))
```

### The openning time
```{r, echo=FALSE, warning=FALSE, message=FALSE}
##opening time of NASDAQ/ EST
time.original <- as.POSIXct(1475587800+60*60, origin = '1970-01-01', tz='EST')
time.original
##data time by 1 minute, 390 minutes
tmp.day <- tmp[60:450,]
time <- seq(time.original, by = "min", length.out = 391)
```

```{r calculate, echo=FALSE, warning=FALSE, message=FALSE}
typical.price <- (tmp.day[,2] + tmp.day[,3] + tmp.day[,4])/3
vp <- tmp.day[,6]*typical.price
total.vp <- cumsum(vp)
total.v <- cumsum(tmp.day[,6])
vwap <- total.vp/total.v
tmp.day <- cbind(tmp.day, typical.price, vp, total.vp, total.v, vwap)
```

### Cleaned data
```{r, echo=FALSE, warning=FALSE, message=FALSE}
##change data to xts form
data.tmp <- xts(tmp.day[,-1], order.by = time)
##rename data
colnames(data.tmp) <- c("CLOSE","HIGH","LOW","OPEN","VOLUME","TYPICALPRICE", "VP", "TOTALVP", "TOTALV", "VWAP")
head(data.tmp)
tail(data.tmp)
```

## Plot of VWAP
When VWAP is over the stock price, it is a long position. The contract is true when VWAP is below.
```{r make datafram complete, echo=FALSE, warning=FALSE, message=FALSE}
##Plot vwap
par(mfrow = c(1,1))
plot(data.tmp$CLOSE, type = "l", main = "AAPL VWAP in 2016-10-04", xlab = "Date", ylab = "AAPL Close Price")
lines(data.tmp$VWAP, col = 2)
legend("topleft", c("VWAP"), col = c(2), lty = 1, pt.cex = 0.8, cex = 1)
```


```{r signal,echo=FALSE, warning=FALSE, message=FALSE}
##We cannot long and short every minutes
## Strategy returns and minute returns
##We take minute returns as close price percentage return by 1 minute. And strategy returns as trade percentage returns.
#when substract between close and vwap is positif, we take short position; the contract is true when it is negatif. 1 is for long
signalfun <- function(x) 
{if(x<0)
  #long
  {return(1)}
 if(x==0)
    {return(0)}
  else 
  #short
   {return(-1)} 
}

```


```{r daily return, echo=FALSE, warning=FALSE, message=FALSE}
#signal
signal <-  data.tmp$CLOSE-data.tmp$VWAP
signal[is.na(signal)] <- 0
trade <- apply(signal, 1, signalfun)
#minute returns/percentage return Close(T)-Close(T-1)/Close(T-1)
minute.return <- Delt(data.tmp$CLOSE, k=1, type = "arithmetic")
#lag is for T, now we calculate return(T+1)
strategy.return <- trade*lag(minute.return,-1)
strategy.return <- na.omit(strategy.return)

```


```{r performance analysis, echo=FALSE, warning=FALSE, message=FALSE, results = 'hide'}
## Performance analyses
#Minute returns are below strategy returns until about 14:57 while a large drop appeared. It shows that strategy returns perform better than the benchmark in most part of time. Drawdown is a percentage to show declination from peak to through. It is a risk indicator. 
analysisvec <- as.zoo(cbind(strategy.return, minute.return))
colnames(analysisvec) <- c("strategyreturn", "minutereturn")
#drawdown is declined percentage from peak to through. risk indicator
#charts.PerformanceSummary(analysisvec, main="Performance of VWAP Strategy", geometric=FALSE, major.ticks="seconds")
```

## Sharp ratio
Sharp ratio is a risk-adjusted rate. It is the average return in excess of risk-free rate per unit of volitality. The sharp ratio of strategy return is a little bit less than that of minute return.
```{r sharp ratio, echo=FALSE, warning=FALSE, message=FALSE}
SharpeRatio(analysisvec)
```

# Mean Reversion Test

Trading strategies can be profitable only if securities prices are either mean-reverting or trending. Prices can be both mean reverting and trending at the same time. Detecting whether the stock has mean reversion property is our goal.\
Mean reverting means that the stochastic part should be stationary and shocks have transitory effects. That means that it should be trend stationary then difference stationary. More generally, stock price will tend to move to the average price over time.
The test method for testing mean reversion is Augmented Dickey-Fuller (ADF) test.

> $H_0 : \gamma = 0 \rightarrow$ there exists unit root $\rightarrow$ the series is difference-stationary, not mean-reverting
$H_A : \gamma < 0 \rightarrow$ there doesn't exist unit root $\rightarrow$ the series is trend-stationary $\rightarrow$ mean-reverting\
The statistic is : 
$$DF = \frac{\hat{\gamma}}{se(\hat{\gamma})}$$
Since it is t-distributed and it is always negative, we reject the null hypothesis when the statistic is less than critical value at certain significant rate. 

> Suppose that $\alpha$ is the significant level. Since it is a one-side test, we have:
$$Pr(\frac{\hat{\gamma}}{se(\hat{\gamma})} > -Z_{\alpha}) = 1-\alpha$$
Thus, the confidence interval is :
$$[-se(\hat{\gamma})*Z_{\alpha}, \, +\infty]$$

We take day time data of GOOG from 2015-08-19. 

```{r , message=FALSE, warning=FALSE, echo = F}
data.mr <- Quandl("GOOG/NASDAQ_GOOGL", start_date="2015-08-19")
data.mr <- data.mr[length(data.mr$Close):1, ]
dataframe<- data.frame(
  Date = data.mr$Date,
  Close = data.mr$Close
)
close  = dataframe$Close
```

## Price tendence
Here is the price tendence :
```{r plot, message=FALSE, warning=FALSE, echo = F}
heading = "Stock Price of Google from 2015-08-19"
plot(close, type = 'l', col = 'blue', main = heading, xlab = "Date", ylab = "Close Price")
```

## T-test Value
Firstly, we use just linear regression to calculate t-test value of the statistics. We want to find out $\gamma$.
$$\Delta y_t=\alpha+\beta t + \gamma y_{t-1} + \delta\Delta y_{t-1} +\epsilon_{t}$$
```{r t test value, message=FALSE, warning=FALSE}

diff.coef <- function(y)
{
#time
t = seq(1:(length(y)-2))

#difference of y_t
y.diff = diff(y)

#difference of y_t
y.t.diff = embed(y.diff, 2)[,1]

#y_t-1
y.t1 = y[2:length(y.diff)]

#difference of y_t-1
y.diff.lag = embed(y.diff, 2)[,2]

formula = lm(y.t.diff ~ t + y.t1 + y.diff.lag)
#summary(formula)

#t-statistic
tsta <- summary(formula)$coefficients[3,3]

#coeff of y_t-1
gamma <- summary(formula)$coefficients[3,1]

return(list(tsta = tsta, gamma = gamma, formula = formula))

}
```
$\alpha = 32.46917, \,\,\beta = 0.01867, \,\,\gamma = -0.04694,\,\, \theta = 0.07291, \,\,t-test statistics = -2.72122$

## Results

Now we use a function from the package 'urca'. In this function, we cannot choose both trend and drift.
```{r, message=FALSE, warning=FALSE, echo = F}
#the object
test.adf = ur.df(close, type = c("trend"), lags = 1)

summary(test.adf)

```
According to the result, the value of t-test statistics is $-2.7212$, not less than critical value at 95% significant level. Thus we cannot reject $H_0$.

And also this function :
```{r, message=FALSE, warning=FALSE, echo = F}
adf.test(close, k=1)
```
t-test statistics is $-2.7212$, p-value = $0.3159$. Thus we cannot reject $H_0$. This series is not mean reverting.

# Half-life of Mean Reversion
Even the process is not mean reverting, in practical trading, we can profit from process that are less certain.Thus, a stock which doesn't pass the ADF test still have chances to be profitable.\
Half-life of mean reversion is to decide how long the price will mean revert. By mathematical deduction, half-life is :
$$H = \frac{\log(2)}{-\gamma}$$

```{r half-life parameter}
#half-life
H <- log(2)/ (-diff.coef(close)$gamma)
H
```
Half of the reversion days will be more than 14 days. That means the process may have a mean reversion in more than 28 days. Therefore, this date can be used to decide our holding period. 

## Cointegration test
Most prices series are not mean reverting or even stationary. However, a linear combination of nonstationary series can be stationary. This kind of series is called cointegrated series. Most common strategies by using cointergration is "pair trading", which means that we long an asset meanwhile we short another one with a certain amount. But cointegration can also be applied to three or more assets' combinations.\

Two tests will be conducted : the Cointergrated Augmented Dickey-Fuller (CADF) test and the Johansen test. The first one is just for two assets while the second one can be used to more assets.

### CADF test
The CADF test has the same principles as the ADF test, the only difference is that the object of the CADF test is the residuals of linear combinations of two nonlinear series. We choose one-day data of EWA (iShares MSCI Australia) and EWC (iShares MSCI Canada) from 2006-04-26 to 2012-04-26.

```{r cadf test, message=FALSE, warning=FALSE, echo = F}
#reference to Ernie Chan's book and Quantstart article
#download data EWA and EWC from quantmod
getSymbols("EWA", from = "2006-04-26", to = "2012-04-26")
getSymbols("EWC", from = "2006-04-26", to = "2012-04-26")

#get adjusted prices
ewa = unclass(EWA$EWA.Adjusted)
ewc = unclass(EWC$EWC.Adjusted)

#plot two series
plot(ewa, type = 'l', main = "Plot of EWA and EWC from 2006-04-26 to 2012-04-26", col = 'red', ylim = c(0, 40), ylab = "EWA & EWC")
lines(ewc, col = 'blue')
#par(new = T)#renew the existed plot
#plot(ewc, type = 'l', col = 'blue')
#par(new = F)

#plot relationship between ewa and ewc
plot(ewc, ewa, main = "Plot EWA and EWC", xlab = "EWA adjusted price", ylab = "EWC adjusted price")
```

```{r linear regression, message=FALSE, warning=FALSE}
#we suppose that there is no intercept
formula.ewa <- lm(ewa ~ 0 + ewc)
res.ewa <- formula.ewa$residuals

formula.ewc <- lm(ewc ~ 0 + ewa)
res.ewc <- formula.ewc$residuals
```

```{r CADF test, message=FALSE, warning=FALSE}
#Attention: we set lag = 1
adf.test(res.ewa, k = 1)
```

```{r ewc, message=FALSE, warning=FALSE}
adf.test(res.ewc, k = 1)
```
Since t-statistic is -3.6042, -3.4192 and p-value of EWA is less than 0.05, we can reject the null hypothese, the residual series is trend stationary which means EWA and EWC are cointegrated with $95\%$ certainty.
We switch independent and dependent variables' position to obtenir better hedge ratio $\beta$. Comparing two results, we choose 
EWA as independent variable because t-statistic and p-value are smaller.

#### Hedge Ratio
Hedge ratio is a value to determine the percentage of hedge. For instance, if we buy 100 lots of EWA, we may sell 70 lots of EWC for hedging.
```{r hedge ratio, message=FALSE, warning=FALSE, echo = F}
hr <- formula.ewa$coefficients
hr
```

### Johansen test
The CADF test can just identify cointegration in pair. However, the Johansen test can test three or more series at the same time. This time, parameters are vectors or matrix. We just consider $lag = 1$.
$$\Delta y_t=M + \Gamma y_{t-1} + A\Delta y_{t-1} +\epsilon_{t}$$
Suppose that $r$ is the rank of $\Gamma$. Obviously, $r$ is from zero to $n$. If all series have unit roots, namely, non-stationary, $r$ is at most $n-1$. However, if there is at least one series is stationary, $r$ can be $n$. $n$ tests are conducted to determine the number of cointegrations. The first null hypothesis is that $r$ is zero which means there is no cointegrations. The first non-zero number is the number of cointegrated series. The $n^{th}$ null hyperthesis is that $r \leq n-1$. 
We add another ETF to this test : IGE (an ETF consisting natural resource stocks). The test function is available in package 'urca'.
```{r johansen test, message=FALSE, warning=FALSE, echo = F, results = 'hide'}
getSymbols("IGE", from = "2006-04-26", to = "2012-04-26")
ige <- unclass(IGE$IGE.Adjusted)
```
```{r test, message=FALSE, warning=FALSE, echo = F}
jo.test <- ca.jo(data.frame(ewa, ewc, ige), K = 2, ecdet = "const", type = "trace", spec = "transitory")
summary(jo.test)
```
The hypothesis $r = 0$ is rejected at the 95% level, while hypotheses $r\leq1$ and $r\leq2$ cannot be rejected. That means EWA and EWC are cointegrated but they do not have cointegration with IGE.\
We test the other three ETFs that tracks an equity index : Standard & Poor's Depository Receipts SPY, the iShares IVV and Vanguard's VOO. 
```{r test etf, message=FALSE, warning=FALSE, echo = F}
#different times get different results, only in 2015 three series are cointegrated
getSymbols("SPY", from = "2015-01-01", to = "2015-11-01")
getSymbols("IVV", from = "2015-01-01", to = "2015-11-01")
getSymbols("VOO", from = "2015-01-01", to = "2015-11-01")

spy = unclass(SPY$SPY.Adjusted)
ivv = unclass(IVV$IVV.Adjusted)
voo = unclass(VOO$VOO.Adjusted)

jo.test.2 <- ca.jo(data.frame(spy, ivv, voo), K = 2, ecdet = "none", type = "trace", spec = "transitory")
summary(jo.test.2)
```
As we can see, three statistics are all larger than values at 95% level. Compared to the first test, now we can get a portfolio consisting three cointegrated ETFs. However, unfortunately, if we change the time of historical data, the results change too. Thus, not all cointegrated will endure for long time. 
 
### Bollinger Band mean reversion strategy
This strategy is referenced to Bollinger Band which uses standard deviation to create long and short signals. While in this strategy, we apply not exactly Bollinger Band but spread Z-Score which is centralized by moving average and centralized by moving standard deviation.
$$Z-Score = \frac{price - moving\,\,average}{moving\,\,standard\,\,deviation}$$
How we use Z-Score to determine buy and sell positions? \
1. If the strategy is conducted for a pair of assets, using hedge ratio to determine the portfolio spread; if the strategy is conducted for more than two assets, using eigenvector in Johansen test to determine the portfolio spread.\
2. Once we get the spread, Z-Score of the spread can be calculated. For determine entry and exit point of each position, we set $entry.value$ and $exit.value$ to control the interval of entry and exit. (*Going long means that we buy low and sell high; going short means that we sell high and buy low.) We decide these two values randomly, $entry.value = 1$ and $exit.value = 0$, which means we conduct long position only when the spread is lower than 1, the vice versa is for short.\
In this case, we choose EWA/EWC as a pair of trading.
```{r bollinger band portfolio, warning=FALSE, echo = F}
portfolio.spread <- res.ewa
portfolio.H <- -log(2)/diff.coef(portfolio.spread)$gamma #***take  halflife of spread

#moving average of spread
portfolio.ma <- filter(portfolio.spread, rep(1/portfolio.H, portfolio.H), sides = 1)
#moving standard deviation of spread
portfolio.sd <- rollapply(portfolio.ma, width = portfolio.H, FUN = sd, fill = NA, align = "right")

#zscore of spread
portfolio.zscore <- (portfolio.spread - portfolio.ma)/portfolio.sd
summary(portfolio.zscore)

#number of non-trading points depending on entry value, here we can choose an entry point larger than 5 based on how many trasactions that we want and more importantly the risks and trading costs
portfolio.exit.count <- sum(abs(portfolio.zscore) < 6, na.rm=TRUE)
portfolio.exit.percentage <- portfolio.exit.count/length(portfolio.spread) 

#set entry value and exit value
portfolio.exit <- 0.5
portfolio.entry <- 6
```
As Z-Score shows, we can choose an entry point larger than 5 based on how many trasactions that we want and more importantly the risks and trading costs, here we take 6. And we take exit value randomly.
```{r cointegration ewa ewc, warning=FALSE, echo = F}
#entry and exit of long or short position
position.long <- (portfolio.zscore <= -portfolio.entry)*1.0
position.short <- (portfolio.zscore >= portfolio.entry)*1.0
position.exit <- (abs(portfolio.zscore) < portfolio.exit)*1.0

#indicator of trading situation: still in long or short position
long.market <- (portfolio.zscore <= -portfolio.exit)*1.0
short.market <- (portfolio.zscore >= portfolio.exit)*1.0
#-1 for short; 0 for no position; 1 for long
position <- short.market - long.market
#create portfolio
#ewa we buy one ewa meanwhile we sell proportional ewc
portfolio.ewa <- ewa*position
#ewc
portfolio.ewc <- -1.0*ewc*position
portfolio.total <- portfolio.ewc + portfolio.ewa

#Percentage return
portfolio.pctreturn <- Delt(portfolio.total)
#delete and change all NA and Inf: great technique! using is.finite()
portfolio.pctreturn[!is.finite(portfolio.pctreturn)] <- 0

#total return
portfolio.return <- cumprod((portfolio.pctreturn + 1)[!(portfolio.pctreturn + 1) %in% 0])
tail(portfolio.return)
```
Here is the return of this portfolio.
```{r pair trading return, warning=FALSE, echo = F}
tail(portfolio.return)
```
Unfortunately, the result is a disaster. We will loss more than our invested money in the end.\


## Questions
1. line 509: Hedge ration is not an, how to define buy and sell lots which are interger?
2. For EWA & EWC pair trading, some parameters can be change.
a. Hedge ratio will change as price change.
b. Buy and sell quantities can also be a parameter to be changed.
c. We choose which period?


## References
[1] Chan, E. (2013). Algorithmic Trading. Wiley.\
[2] Anon, (2016). [online] Available at: http://www.jerrydwyer.com/pdf/Clemson/Cointegration.pdf [Accessed 4 Nov. 2016].\
[3] R-forge.r-project.org. (2016). [online] Available at: https://r-forge.r-project.org/scm/viewvc.php/*checkout*/pkg/inst/doc/IntroductionToPairTrading.pdf?revision=6&root=pairtrading&pathrev=6 [Accessed 4 Nov. 2016].\
[4] Anon, (2016). [online] Available at: http://www.jerrydwyer.com/pdf/Clemson/Cointegration.pdf [Accessed 4 Nov. 2016].